Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-16 icse/paper.tex
Paper

\subsection{Gapped clones} \label{sec:t3r}
%Explain type 3, why it is not always refactorable, solution
Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}. When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''. ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s). We define the following methods to refactor such clones:
\begin{itemize}
  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
  \item We use a lambda function to pass the difference in statements from each location of the clone.
\end{itemize}
Again, a trade-off is at play, as these solutions increase the complexity in favor of removing a clone.

>>>>

\subsection{Gapped clones} \label{sec:t3r}
%Explain type 3, why it is not always refactorable, solution
Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}. When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones'' \cite{ueda2002detection, zhao2018automatic}. ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s). We define the following methods to refactor such clones:
\begin{itemize}
  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
  \item We use a lambda function to pass the difference in statements from each location of the clone.
\end{itemize}
For both refactoring techniques a trade-off is at play, as these solutions increase the complexity and volume of the source code in favor of removing a clone.
